Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-21 article.rnw
Correct spelling.

Additionally, studies that use grouping to simplify models of species interactions have always made one untested assumption: that the same grouping is equally valid for how species affect others as for how spcies respond to others \parencite{XXX}.
There is good reason to question this assumption, as it is known that different traits can govern species' competitive effects than govern their responses to competition \parencite{goldberg1991competitive}.
As such, the best groupings of species may be different for each of the effects and responses.

>>>>

Additionally, studies that use grouping to simplify models of species interactions have always made one untested assumption: that the same grouping is equally valid for how species affect others as for how species respond to others \parencite{XXX}.
There is good reason to question this assumption, as it is known that different traits can govern species' competitive effects than govern their responses to competition \parencite{goldberg1991competitive}.
As such, the best groupings of species may be different for each of the effects and responses.
